Implications of afforestation policies for global markets

### 2023-05-31 paper.Rmd
Update paper.Rmd

>>>>

South America and Sub-Saharan Africa are two regions that show much potential for afforestation. It is estimated that these two regions hold at least 50% of the potential global gain while regions such as Northern Africa and the Middle East show little promise as growth rates are quite low [@doelman2020]. Thus, it is promising that the African Forest Landscape Restoration Initiative (AFR100) aims to afforest 100 million hectares by 2030 with roughly 70 percent of the committments coming from Sub-Saharan nations [@auda2023]. However, while many of these nations may be well-suited in big-physical terms for afforestation, they also may be politically unstable or border regions of instability. This creates concern about how long-lasting any investment may be. Other nations that have a big potential for gains from afforestation face different challenges. India has a great potential to increase its carbon sequestration through afforestation, but due to its masssive population and food security worries, its NDC does not entertain the idea of agricultural land being repurposed and instead primarily considers wastelands that may not be well suited for afforestation [@amjath2019].
These are not the only concerns that need to be considered by policymakers planning afforestation activities, as for example, oelman2020].
